Weakly Nonlinear Analysis of the Standard and Helical Magnetorotational Instabilities in a Taylor Couette Flow

### 2016-07-26 paper/widegap_mri_paper.tex
one more run

Because of the MRI's complexity, analytical treatments of the MRI use some combination of convenient approximations: ideal MHD, linearized equations, expedient boundary conditions, and simplified geometries. In particular, much of the analytical work on MRI saturation has focused on local approximations, often representing a section of a disk by solving the MHD equations in an isolated region subject to shear periodic boundary conditions (the ``shearing box"). While the MRI is a local instability, certain properties of the local problem are not generic to the global problem. In the shearing box, linear evolution is dominated by a class of MRI mode known as channel modes.  %Channel modes, a class of MRI mode that dominates MRI evolution and saturation in the local approximation, are artificially over-prominent in the shearing box (e.g. \citei{Latter:2015}).

@@

>>>>

Because of the MRI's complexity, analytical treatments of the MRI use some combination of convenient approximations: ideal MHD, linearized equations, expedient boundary conditions, and simplified geometries. In particular, much of the analytical work on MRI saturation has focused on local approximations, often representing a section of a disk by solving the MHD equations in an isolated region subject to shear periodic boundary conditions (the ``shearing box"). While the MRI is a local instability, certain properties of the local problem are not generic to the global problem. In the shearing box, linear evolution is dominated by a class of MRI mode known as channel modes.  %Channel modes, a class of MRI mode that dominates MRI evolution and saturation in the local approximation, are artificially over-prominent in the shearing box (e.g. \citei{Latter:2015}). 
These are linear modes which also happen to be exact solutions to the \textit{nonlinear} local MRI equations. Runaway growth is avoided in this paradigm by the instability of the channel modes themselves, which are destroyed by parasitic (secondary) instabilities (\citei{Goodman:1994ul}, \citei{Pessah:2010ic}).

@@

\bibitem[Pessah(2010)]{Pessah:2010ic}
Pessah, M, 2010, ApJ, 716, 1012
